\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A Radial Time Projection Chamber for $\alpha$ detection in CLAS at JLab}

### 2017-11-06 eg6-letters/NIM/EG6_RTPC_NIM.tex
Starting on the review of NIM

Until recently, the Thomas Jefferson National Accelerator Facility, in 
Newport News, Virginia, USA, has provided high power electron beams of 
up to 6 GeV energy and 100$\%$ duty factor to three experimental Halls (A, B, C) 
simultaneously. The CLAS spectrometer~\cite{Mecking:2003zu}, located
in Hall-B, was based on a superconducting toroidal magnet and composed of 
several sub-detectors. Figure~\ref{fig:CLAS} shows a three dimensional 
representation of the baseline CLAS spectrometer:
\begin{itemize}
 \item Three regions of Drift Chambers (DC) for the tracking of charged 
       particles~\cite{Mestayer:2000we}.
 \item Superconducting toroidal magnet to bend the trajectories 
       of charged particles, thus allowing momentum measurement with the DC tracking information.
 \item Threshold Cherenkov Counters (CC) for electron identification at momenta 
    $<2.7$ GeV/c~\cite{Adams:2001kk}.
 \item Scintillation Counters (SC) to identify charged hadrons by measuring their 
       time of flight~\cite{Smith:1999ii}.
 \item Electromagnetic Calorimeters (EC) for identification of electrons, 
       photons and neutrons~\cite{Amarian:2001zs}.
\end{itemize}

@@

With a 6 GeV incident electron energy, the recoiling $^{4}$He nuclei from 
coherent DVCS have an average momentum around 300~MeV/c (12~MeV kinetic 
energy). Such low energy $\alpha$ particles are stopped very rapidly, so the 
RTPC was designed to be as close as possible to the target and fit inside the 
230~mm diameter shell and cryostat wall of the solenoid magnet bore.

@@

One of the important challenges in developing the RTPC was to obtain a good 
support structure for the GEM foils to allow a tractable installation of the 
GEMs. At the same time, we wanted to keep the material budget small in the 
forward region where we detect other particles in subsequent detectors. We 
successfully realized these prerequisites by using fiber glass rings glued to 
each end of the GEM foils to form self supporting cylinders that could be 
installed independently in the RTPC after gluing and soldering operations. The 
rigidity of the GEM foils was enough for the structure to be self-supporting 
and only the upstream end of the cylinder was fixed to the main mechanical 
support structure. This design only left a light fiberglass ring in the 
downstream end, reducing to a minimum secondary interactions.

>>>>

Until recently, the Thomas Jefferson National Accelerator Facility, in 
Newport News, Virginia, USA, has provided high power electron beams of 
up to 6 GeV energy and 100$\%$ duty factor to three experimental Halls (A, B, C) 
simultaneously. The CEBAF Large
Acceptance Spectrometer (CLAS)~\cite{Mecking:2003zu}, located
in Hall-B, was based on a superconducting toroidal magnet and composed of 
several sub-detectors. Figure~\ref{fig:CLAS} shows a three dimensional 
representation of the baseline CLAS spectrometer:
\begin{itemize}
 \item Three regions of Drift Chambers (DC) for the tracking of charged 
       particles~\cite{Mestayer:2000we}.
 \item Superconducting toroidal magnet to bend the trajectories 
       of charged particles, thus allowing momentum measurement with the DC tracking information.
 \item Threshold Cherenkov Counters (CC) for electron identification at momenta 
    $<2.7$ GeV/c~\cite{Adams:2001kk}.
 \item Scintillation Counters (SC) to identify charged hadrons by measuring their 
       time of flight~\cite{Smith:1999ii}.
 \item Electromagnetic Calorimeters (EC) for identification of electrons, 
       photons and neutrons~\cite{Amarian:2001zs}.
\end{itemize}

@@

With a 6 GeV incident electron energy, the recoiling $^{4}$He nuclei from 
coherent DVCS have an average momentum around 300~MeV/c (12~MeV kinetic 
energy). Such low energy $\alpha$ particles are stopped very rapidly, so the 
RTPC was designed to be as close as possible to the target and fit inside the 
230~mm diameter shell and cryostat wall of the solenoid magnet bore of the 
CLAS.

@@

The main structural improvement compared to the 2005 RTPC~\cite{Fenker:2008zz} 
was to obtain a better support structure for the GEM foils. In the previous version,
the RTPC was essencially composed of two independent half-cylinder separated
by their own structures. In these, the installation of the GEM was not very practical
and wrinkles were visibles on the GEM surfaces. To allow for a better installation 
and, at the same time, keep the mechanical structure out of the drift volume, 
the present design is based on GEM cylinder. This improves the acceptance of the
overall detector and reduces the material budget in the 
forward region, where we detect other particles in CLAS. We 
realized these cylinders by using fiber glass rings glued to 
each ends of the GEM foils to form self supporting pieces that could be 
installed independently in the RTPC after gluing and soldering operations. The 
rigidity of the GEM foils was enough for the structure to be self-supporting 
and only the upstream end of the cylinder was fixed to the main mechanical 
support structure. This design only left a light fiberglass ring in the 
downstream end, reducing to a minimum secondary interactions.

### 2017-11-06 eg6-letters/NIM/review-1/review-1.tex
Starting on the review of NIM

%\documentclass[a4paper,11pt,twoside]{ThesisStyle}
\documentclass[a4paper,11pt,twoside]{article}

@@

\subsection*{Chapter 2}
\item As already said I would not speak of cylindrical GEMs but 
   semi-cylindrical. Moreover, please add the reference to Sauli's paper [11] 
   when speaking the first time about GEM in the text.\\
\textcolor{blue}{cylinderical GEMs-> semi-cylinderical. The reference has been added.}

\item In my opinion, this chapter should highlight better which are the 
   improvements w.r.t. BoNuS detector to underline the originality of this 
   work. For example, better acceptance? Higher gain? Higher electric 
   stability? Lower material budget? Please quote some old and new values, 
   maybe in a table, to make them evident.\\
\textcolor{red}{To the group: Do we have such a comparison? }

\item Relevant length and thicknesses of the various elements are reported in 
   the text and in the figure, can you please add also the z position of the 
   target w.r.t the detector? To give the complete information, I would also 
   add the value of the induction gap electric field, which is the only missing 
   field value and the value of the reached amplification gain with the three 
   GEM.\\
\textcolor{blue}{- The target tube is the central z-axis of the detector. The 
text is modified to make it clean.\\}
\textcolor{red}{- Regarding the electric field, it was 2.8 kV/cm in BoNuS, does 
anyone know our exact field in this gap?\\}
\textcolor{blue}{- The gain of such GEM configuration has been studied by 
   CERN's Gas Detector Development Group (Fabio Sauli, Progress with the Gas 
   Electron Multiplier, 2nd Workshop on Advanced Transition Radiation Detectors 
   for Accelerator and Space Applications (Bari, Sept. 4-7, 2003), Nucl. Instr. 
   and Meth. A522(2004)93). The results, see the reference, demonstrate that 
one should not simply add gains to each other for multilayer GEM 
amplifications.  We did not evaluate precisely the overall gain in our chamber, 
so we do not have a value for our RTPC GEM system at this point.}

@@

\subsection*{ Chapter 4}
	/paragraph 4.1
\item I would really prefer to call it drift "velocity" instead of drift 
   "speed"\\
\textcolor{red}{To the group: We do have radial and azimuthal drift velocities, 
but we measure the average of their sum. }

\item I don't really understand the procedure to find the drift velocity 
   described here and fig. 7. What is $Nb_{max}$ and $Nb_{max/2}$? Why does 
   $T_{max/2}$ correspond to $Nb_{max/2}$ and why is it used as $T_{max}$? If I 
   make a quick calculation and use $T_{max}$ ~ 65 * 100ns and a drift length 
   of ~ 3cm /cos(23°) ~ 7.5 cm I get a $v_{drift}$ ~ 1.15 cm/microsec << 5 
   cm/microsec which is the average value of drift velocity in drift 
   chambers.\\
The procedure according to me would be:\\
- for each hit associated to a track, whose time information is available, take 
the drift time $t_{drift_{i}}$;\\
- plot the distribution of these $t_{drift_{i}}$;\\
- find the $T_{min}$ = minimum $t_{drift_{i}}$ and $T_{max}$ = maximum 
$t_{drift_{i}}$\\
- compute $delta_{t} = T_{max} - T_{min}$ and extract the drift velocity by 
dividing the track length / $delta_{t}$. Figure 8 would have the $delta_{t}$ 
instead of the $T_{max}$ vs z.\\
Please provide more details on the applied procedure, since I have the open 
questions I wrote before and I could not understand it properly. Moreover, 
please quote the value of the found drift velocity. Is it in accordance with 
the simulations?\\
\textcolor{blue}{ }

\item Figure 6: why are $T_{min}$ and $T_{max}$ not at the drift gap 
   extremities?\\
   \textcolor{blue}{This is a schematic to illustrate the definitions of 
   $T_{min}$ and $T_{max}$ in a chain of hits. The figure can be modified if 
needed.}

>>>>

\documentclass[a4paper,11pt,twoside]{article}

@@

\subsection*{Chapter 2}
\item As already said I would not speak of cylindrical GEMs but 
   semi-cylindrical. Moreover, please add the reference to Sauli's paper [11] 
   when speaking the first time about GEM in the text.\\
\textcolor{blue}{cylindrical GEMs-> semi-cylindrical. The reference has been added.}

\item In my opinion, this chapter should highlight better which are the 
   improvements w.r.t. BoNuS detector to underline the originality of this 
   work. For example, better acceptance? Higher gain? Higher electric 
   stability? Lower material budget? Please quote some old and new values, 
   maybe in a table, to make them evident.\\
\textcolor{blue}{The main difference is in the design of the structure, this has 
been made clearer in this chapter.}

\item Relevant length and thicknesses of the various elements are reported in 
   the text and in the figure, can you please add also the z position of the 
   target w.r.t the detector? To give the complete information, I would also 
   add the value of the induction gap electric field, which is the only missing 
   field value and the value of the reached amplification gain with the three 
   GEM.\\
\textcolor{red}{- The target tube is the central z-axis of the detector. The 
text is modified to make it clean. Raph: He understands that, he asks what is the z position.\\}
\textcolor{red}{- Regarding the electric field, it was 2.8 kV/cm in BoNuS, does 
anyone know our exact field in this gap? Raph: This is indicated already, I am not sure what he
means by "induction gap"\\}
\textcolor{red}{We did not evaluate precisely the overall gain in our chamber.
Can we quote a value from comparison with Bethe-Heitler or GEANT4?}

@@

\subsection*{ Chapter 4}
	/paragraph 4.1
\item I would really prefer to call it drift "velocity" instead of drift 
   "speed"\\
\textcolor{red}{To the group: We do have radial and azimuthal drift velocities, 
but we measure the average of their sum. Raph: What is the link with the question?}

\item I don't really understand the procedure to find the drift velocity 
   described here and fig. 7. What is $Nb_{max}$ and $Nb_{max/2}$? Why does 
   $T_{max/2}$ correspond to $Nb_{max/2}$ and why is it used as $T_{max}$? If I 
   make a quick calculation and use $T_{max}$ ~ 65 * 100ns and a drift length 
   of ~ 3cm /cos(23°) ~ 7.5 cm I get a $v_{drift}$ ~ 1.15 cm/microsec << 5 
   cm/microsec which is the average value of drift velocity in drift 
   chambers.\\
The procedure according to me would be:\\
- for each hit associated to a track, whose time information is available, take 
the drift time $t_{drift_{i}}$;\\
- plot the distribution of these $t_{drift_{i}}$;\\
- find the $T_{min}$ = minimum $t_{drift_{i}}$ and $T_{max}$ = maximum 
$t_{drift_{i}}$\\
- compute $delta_{t} = T_{max} - T_{min}$ and extract the drift velocity by 
dividing the track length / $delta_{t}$. Figure 8 would have the $delta_{t}$ 
instead of the $T_{max}$ vs z.\\
Please provide more details on the applied procedure, since I have the open 
questions I wrote before and I could not understand it properly. Moreover, 
please quote the value of the found drift velocity. Is it in accordance with 
the simulations?\\
\textcolor{red}{Raph: I will modify the text for this.}

\item Figure 6: why are $T_{min}$ and $T_{max}$ not at the drift gap 
   extremities?\\
   \textcolor{red}{This is a schematic to illustrate the definitions of 
   $T_{min}$ and $T_{max}$ in a chain of hits. The figure can be modified if 
needed. Raph: Are you asking him if he insists? We need to fix the figure.}
